---
title: "OSHA Analysis Template"
date: "11/25/2020"
author: "Your Name"
output:
  html_document:
    code_folding: hide
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

Provide a brief summary of the purpose of this document and high-level findings.

## Load libraries

Code to load necessary libraries. Click "Code" button to view.

```{r message=FALSE, echo=TRUE, warning=FALSE}
# For general data science work
library(tidyverse)

# For data cleaning
library(janitor)

# For writing data to google sheets
library(gargle)
library(googlesheets4)
#source("keys/keys.R")

# For fancy tables
# library(DT)
# library(kableExtra)

# # For producing html files
# library(knitr)

```

## Load and clean data

Describe the data you are loading here. 

Click "Code" button to view scripts to load data.

```{r message=FALSE, echo=TRUE, warning=FALSE}

# Write code to load necessary data 
#open_complaints <- read_csv("RMD/data/closed_complaints_labeled.csv")
open_complaints <- rio::import("closed_complaints.xlsx", skip=3)
# Write code to clean necessary data, if cleaning required. 
open_complaints <- open_complaints %>%
  clean_names()
```

## Analyze data

Brief description of analysis goes here. 

### Analyze data section title

Brief description of specific analysis and results, as output by the code block below this section. 

```{r message=FALSE, echo=TRUE, warning=FALSE}

# Example
# Group and count by state
state_count <- open_complaints %>%
  group_by(site_state) %>%
  summarise(count_open_complaints = n()) %>%
  arrange(desc(count_open_complaints))

# Display the result in le fancy datatable format
# Lots of customizable options https://rstudio.github.io/DT/
state_count %>%
  datatable()

```

## Export data

Brief description of dataframes to export to Google Sheets for global sharing. 

```{r message=FALSE, echo=TRUE, warning=FALSE}
# https://googlesheets4.tidyverse.org/
#workbook_id <- 
  
# Build a list of dataframes to write to google sheets
list_of_dataframes <-  list(state_count)

# Create a Google Sheets workbook
example_workbook_name <- gs4_create("example_osha_workbook", sheets=list_of_dataframes)

# Get the ID
example_workbook_url <- unclass(example_workbook_name)
example_workbook_url <- paste0(
  "https://docs.google.com/spreadsheets/d/",
  example_workbook_url
)
example_workbook_url





```
